Full Article Review

### 2024-07-05 doc/reviews/luke.qmd
chore: recreated the docs for reviewing

<!-- Write your notes down here -->

>>>>

## General themes

::: content-hidden
Look for what the paper is generally about and some basic overall themes and
topics in the paper.
:::

## Type of paper

::: content-hidden
Is it a guide, community-building, an example of a workflow, etc.
:::

## Other notes

::: content-hidden
What we found was interesting or what we'd like to share, discuss, or
present in the main scoping review paper.
:::
